---
title: "Dash Final"
output: flexdashboard::flex_dashboard
runtime: shiny
---



```{r global, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(shiny)
library(DT)
library(gt)

video_games <- read_csv("data/video_games_updated.csv")

term_data <- read_csv("data/term_freq.csv")

sentiment_data <- read.csv("data/sentiment_scores.csv")

genre_choices <- c("Action", "Adventure", "Massively Multiplayer", "Free To Play", 
                   "RPG", "Indie", "Early Access", "Strategy", "Casual", 
                   "Simulation", "Sports", "Racing")

```


Home
==========================
```{r, echo=FALSE}
img_url <- video_games$main_img[round(runif(1,1,398))]
  
```


Video games are one of the fastest-growing entertainment industries in the world, generating
billions in revenue and attracting audiences across every demographic. But how do critics and
players actually agree or maybe disagree on what critria makes a game good?

In This dashboard we explore video game data across genres, platforms, and time using
three distinct rating systems:

- **Metacritic Score** — an aggregated critic score (0–100)
- **IGN Score** —  A editorial scores (0–10)  
- **Community Score** — user-submitted ratings reflecting player sentiment (0–10)

We hope that by comparing these sources side by side with the different critria, we can uncover patterns in how different genres are received and what makes games better.

We also will do some text analysis to see patterns in user submitted text steam reviews 

```{r}
knitr::include_graphics(img_url)
```


Row
-------------------------

### About Us

This project was created by Sam Brumbaugh, and Henry Norton-Bower.

All source code for this project is located [in this git repo](https://github.com/HenryN-B/Mini-Project-2)

Row
-------------------------

### Data & Sources

The dataset used in this project was created and compiled by Sam, and Henry using API calling and web scraping on 2 main sources.

- Using the steam API [from the steam store](https://store.steampowered.com).
- Scraping the [IGN game review page](https://www.ign.com/reviews/games).

To scrape this data we first had to hand compile a list of 400 steam app id's which is a number associated with every steam game. We explored ways to automate this process, but in the end we where not getting the results we wanted. Maybe in future work this is sometime we could explore further. 

The list of game was the top 400 games with the highest peak player count after accounting for bot activity. With this list we first scraped all of the steam data, then used the game names to scrape the IGN data.

Genres
==========================

Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
inputPanel(
  selectInput("genre", label = "Genre(s)",
              choices  = genre_choices,
              selected = NULL,
              multiple = TRUE),
  selectInput("reviewType", label = "Select Review Type",
              choices = c("Metacritic Score" = "metacritic_score", 
            "IGN Score" = "ign_score", 
            "Community Score" = "community_score"),
              selected = "ign_score"))
```


Row
-------------------------

Video game scores can vary widely depending on the genre and fast-paced Action titles may be judged differently than slower RPGs. To investigate whether these differences are statistically meaningful, we compare review scores across genres using three distinct rating sources: Metacritic (a critic aggregator), IGN (editorial), and Community (user-submitted). Select one or more genres and a review type to explore the distributions below.


### Visualization Between Genres.
```{r echo = FALSE}

selected_genres <- reactive({
  if (is.null(input$genre) || length(input$genre) == 0) {
    genre_choices                        
  } else {
    input$genre
  }                    
})

score_labels <- c(
  metacritic_score = "Metacritic Score (0–100)",
  ign_score        = "IGN Score (0–10)",
  community_score  = "Community Score (0–10)"
)

video_games_no_na <- video_games |>
  filter(!is.na(ign_score) | ign_score != "NR" |
           !is.na(metacritic_score) | !is.na(community_score)) |>
  mutate(ign_score = as.numeric(ign_score),
         metacritic_score = as.numeric(metacritic_score),
         community_score = as.numeric(community_score))


filtered_data <- reactive({
  video_games_no_na |>
    separate_rows(genres, sep = ", ") |>
    filter(str_detect(genres, str_c(selected_genres(), collapse = "|")) &
             !is.na(.data[[input$reviewType]]))
})

anova_caption <- reactive({
  if (length(selected_genres()) > 1) {
    fit   <- lm(as.formula(paste(input$reviewType, "~ genres")), data = filtered_data())
    f_val <- anova(fit)[["F value"]][1]
    p_val <- anova(fit)[["Pr(>F)"]][1]
    
    p_text <- if (p_val < 0.001) "p < 0.001" else paste0("p = ", round(p_val, 3))
    
    str_c("Avova test: p-vlaue: ", p_text, " and F value: ", round(f_val,3),". 
                           If p-value is less than 0.05 then difference in means is significant.")
  } 
})

renderPlot({
  video_games_no_na |>
    separate_rows(genres, sep = ", ") |>
    filter(str_detect(genres, str_c(selected_genres(), collapse = "|")) 
           & !is.na(ign_score) 
           & ign_score != "NR") |>
    ggplot(aes(x = genres, y = .data[[input$reviewType]], fill = genres)) +
    geom_boxplot(outlier.alpha = 0.4) +
    geom_jitter(width = 0.2, alpha = 0.2) +
    theme_bw() +
    labs(
      x     = "Genre",
      y     = score_labels[input$reviewType],
      title = str_c("Distribution of ", score_labels[input$reviewType], " by Genre"),
      fill  = "Genre",
      caption = anova_caption()
    ) 
})
```


Reviews
==========================


Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
inputPanel(
  selectInput("yvars",
    label = "Select The Y axis:",
    choices = c(
      "player_count" = "player_count",
      "metacritic_score" = "metacritic_score",
      "ign_score" =  "ign_score",
      "community_score" = "community_score"), selected = "player_count")
    )

```


Row
-------------------------

We wanted to see how a game's price affects its ratings. To investigate this we will explore the relationship between price and ratings using smoother line plots. While player count is not a traditional rating it is an interesting secondary kind of rating.

### Visualization of How Price Affects Ratings
```{r echo = FALSE}
renderPlot({
  req(input$yvars)
  
  video_games |>
    filter(
      !is.na(ign_score),
      ign_score != "NR",
      community_score != "-", 
    ) |>
    ggplot(aes(x = price, y = as.numeric(.data[[input$yvars]]))) +
    geom_smooth(se=FALSE)+
    labs (x= "Price (USD)", y= "Your Choice Rating")+
    theme_bw()
})

```

Row
-------------------------

Another consideration is if professional reviews agree with the people they purport to represent. We can represent this with a jittered scatter plot.

### Visualization of Professional Ratings and Community Ratings
```{r echo=FALSE}
  video_games |>
    filter(
      !is.na(ign_score),
      ign_score != "NR",
      community_score != "-",
      !is.na(metacritic_score)
    ) |>
  mutate(
    dev_score = (as.numeric(ign_score)*10 + as.numeric(metacritic_score)) / 2
  )|>
    ggplot(aes(x = community_score, y = dev_score)) +
    geom_smooth(se=FALSE, method = lm)+
    geom_jitter(size = 0.9, alpha = 0.4, width = .5)+
    labs(x = "Community Rating", y = "Professional Rating") +
    theme_bw()

```


Text Analysis {data-orientation=rows}
==========================

Row {data-height=70}
-------------------------------------

We also thought that doing some text analysis would provide interesting insights because Steam reviews can give us direct, unfiltered player opinions at scale. This tab uses data from thousands of user reviews to explore patterns in how players talk about games. Though before proceeding a few things to consider is that from all reviews to weed out non quality reviews, we filtered reviews that had less then 5 words, less then 20 characters , or more then 5 repeating letters. We also deleted repeated reviews.


Row {.tabset .tabset-fade}
-------------------------------------
### Sentiment

```{r echo =FALSE}
renderPlot({sentiment_data |>
  ggplot(aes(x= reorder(genres, sentiment_score),
             y = sentiment_score,
             fill = sentiment_score > 0)) +
  geom_col(show.legend = FALSE) + 
 geom_hline(yintercept = 0, linewidth = 0.5, color = "grey40") +
  scale_fill_manual(values = c("TRUE" = "darkgreen", "FALSE" = "darkred")) +
  coord_flip() +
  labs(
      title    = "Net Avg Sentiment Score by Genre",
      x = NULL,
      y = "Net Sentiment Score"
    ) +
    theme_bw()
})

```

### Term Frequency
```{r echo=FALSE}
fillRow(
  flex = c(1, 3),
  selectInput("genre_term", label = "Genre",
              choices = genre_choices,
              selected = "Action"),
  gt_output("termTable")
)
```

```{r echo=FALSE}
output$termTable <- render_gt({
  req(input$genre_term)
  term_data |>
    filter(genres == input$genre_term) |>
    arrange(desc(tf_idf)) |>
    slice_head(n= 10) |>
    gt() |>
    tab_header(title = paste("Top Terms —", input$genre_term)) |>
    cols_label(
      word   = "word",
      tf     = "Term Freq",
      idf    = "IDF",
      tf_idf = "TF-IDF Score"
    ) |>
    fmt_number(
      columns = c(tf, idf, tf_idf),
      decimals = 4
    )
})
```

### Temp

Text Here

Full Database
==========================

Inputs {.sidebar}
-------------------------
```{r, echo=FALSE}
inputPanel(
  selectInput("genre_db", label = "Genre(s)",
              choices = c(genre_choices), 
              selected = NULL, multiple = TRUE),
  sliderInput("price", label = "Price Range", min = 0, max = 100, value = c(0,100)),
  
  checkboxGroupInput("platform", label= "Playable Platforms", c("Windows", "Mac", "Linux"), selected =  c("Windows", "Mac", "Linux"), inline = T))
```


Column
-------------------------------------

### Games

```{r echo = FALSE}

selected_genres <- reactive({
  if (is.null(input$genre_db) || length(input$genre_db) == 0) {
    genre_choices                        
  } else {
    input$genre_db
  }                    
})


filtered_games <- reactive({
  video_games |>
    filter(
      price >= input$price[1],
      price <= input$price[2],
      str_detect(genres, str_c(selected_genres(), collapse = "|")),
      ("Windows" %in% input$platform & isWindows == 1) |
      ("Mac" %in% input$platform & isMac == 1) |
      ("Linux" %in% input$platform & isLinux == 1)
    ) |>
    select(
      "Name"            = name,
    "Price"           = price,
       "Release Date"    = release,
      "Developer"       = developer,
      "Publisher"       = publisher,
      "IGN Score"       = ign_score,
      "Community Score" = community_score,
     main_img
    )
})

renderDT({
  filtered_games() |>
    mutate(main_img = str_c('<img src="', main_img, '" height="90"/>')) |>
    datatable(
      escape = FALSE,
      options = list(
        pageLength = 15,
        scrollX = FALSE,
        autoWidth = TRUE
      ),
      rownames = FALSE
    )
})
```