---
title: "Dash Final"
output: flexdashboard::flex_dashboard
runtime: shiny
---



```{r global, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(shiny)

video_games <- read_csv("data/video_games_updated.csv")
```

Home
==========================
```{r, echo=FALSE}
img_url <- video_games$main_img[round(runif(1,1,398))]
  
```


Video games are one of the fastest-growing entertainment industries in the world, generating
billions in revenue and attracting audiences across every demographic. But how do critics and
players actually agree or maybe disagree on what critria makes a game good?

This dashboard explores video game data across genres, platforms, and time using
three distinct rating systems:

- **Metacritic Score** — an aggregated critic score (0–100)
- **IGN Score** —  A editorial scores (0–10)  
- **Community Score** — user-submitted ratings reflecting player sentiment (0–10)

We hope that by comparing these sources side by side, we can uncover patterns in how different genres are received.

```{r}
knitr::include_graphics(img_url)
```


Row
-------------------------

### About Us

This project was created by Sam Brumbaugh, and Henry Norton-Bower.

All source code for this project is located [https://github.com/HenryN-B/Mini-Project-2](In this git repository)

Row
-------------------------

### Data & Sources

**Will add stuff later.**

Genres
==========================

Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
inputPanel(
  selectInput("genre", label = "Select Genre(s)",
              choices = c("Action", "Adventure", "Massively Multiplayer", "Free To Play", "RPG", "Indie", "Early Access", "Strategy", "Casual", "Simulation", "Sports", "Racing"), 
              selected = "Action", multiple = TRUE),
  selectInput("reviewType", label = "Select Review Type",
              choices = c("Metacritic Score" = "metacritic_score", 
                          "IGN Score" = "ign_score", 
                          "Community Score" = "community_score"),
              selected = "ign_score"))
```


Row
-------------------------

Video game scores can vary widely depending on the genre and fast-paced Action titles may be judged differently than slower RPGs. To investigate whether these differences are statistically meaningful, we compare review scores across genres using three distinct rating sources: Metacritic (a critic aggregator), IGN (editorial), and Community (user-submitted). Select one or more genres and a review type to explore the distributions below. Also When exactly two genres are selected, a  two-sample t-test is reported and for three or more, a ANOVA test is used instead.


### Visualization Between Genres.
```{r echo = FALSE}

score_labels <- c(
  metacritic_score = "Metacritic Score (0–100)",
  ign_score        = "IGN Score (0–10)",
  community_score  = "Community Score (0–10)"
)

video_games_no_na <- video_games |>
  filter(!is.na(ign_score) | ign_score != "NR" |
           !is.na(metacritic_score) | !is.na(community_score)) |>
  mutate(ign_score = as.numeric(ign_score),
         metacritic_score = as.numeric(metacritic_score),
         community_score = as.numeric(community_score))





renderPlot({
  video_games_no_na |>
    separate_rows(genres, sep = ", ") |>
    filter(str_detect(genres, str_c(input$genre, collapse = "|")) 
           & !is.na(ign_score) 
           & ign_score != "NR") |>
    ggplot(aes(x = genres, y = .data[[input$reviewType]], fill = genres)) +
    geom_boxplot(outlier.alpha = 0.4) +
    theme_bw() +
    labs(
      x     = "Genre",
      y     = score_labels[input$reviewType],
      title = str_c("Distribution of ", score_labels[input$reviewType], " by Genre"),
      fill  = "Genre"
    ) 
})
```


Reviews
==========================


Inputs {.sidebar}
-------------------------

```{r, echo=FALSE}
inputPanel(
  selectInput("yvars",
    label = "Select The Y axis:",
    choices = c(
      "player_count" = "player_count",
      "metacritic_score" = "metacritic_score",
      "ign_score" =  "ign_score",
      "community_score" = "community_score"), selected = "player_count")
    )

```


Row
-------------------------

We wanted to see how a game's price affects its ratings. To investigate this we will explore the relationship between price and ratings using smoother line plots. While player count is not a traditional rating it is an interesting secondary kind of rating.

### Visualization of How Price Affects Ratings
```{r echo = FALSE}
renderPlot({
  req(input$yvars)
  
  video_games |>
    filter(
      !is.na(ign_score),
      ign_score != "NR",
      community_score != "-"
    ) |>
    ggplot(aes(x = price, y = as.numeric(.data[[input$yvars]]))) +
    geom_smooth(se=FALSE)+
    labs (x= "Price (USD)", y= "Your Choice Rating")+
    theme_bw()
})

```

Row
-------------------------

Another consideration is if professional reviews agree with the people they purport to represent. We can represent this with a jittered scatter plot.

### Visualization of Professional Ratings and Community Ratings
```{r echo=FALSE}
  video_games |>
    filter(
      !is.na(ign_score),
      ign_score != "NR",
      community_score != "-",
      !is.na(metacritic_score)
    ) |>
  mutate(
    dev_score = (as.numeric(ign_score)*10 + as.numeric(metacritic_score)) / 2
  )|>
    ggplot(aes(x = community_score, y = dev_score)) +
    geom_smooth(se=FALSE, method = lm)+
    geom_jitter(size = 0.9, alpha = 0.4, width = .5)+
    labs(x = "Community Rating", y = "Professional Rating") +
    theme_bw()

```



Text analysis 
==========================
WIP

Full Database
==========================

WIP

*Ideas*
**Player count vs number of reviews**
